\chapter*{List of Figures}
{\color{purple}\titlerule[2.5pt]}
\vspace{4pc}%

\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:neutrinos}} on page~\pageref{chap:neutrinos}: \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Illustration of neutrinos by \textsf{Sandbox Studio}, Chicago. \textbf{Credit:} \textbf{Ana Kova}. Original artwork at \url{http://www.symmetrymagazine.org/article/the-hidden-neutrino}. Can you spot the sterile in the bunch? \\
\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:cosmology}} on page~\pageref{chap:cosmology}:  \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Artist illustration of the observable universe. Distances from the Observer in the center to the edge of the observable Universe on the periphery is logarithmic-scaled. I especially enjoy this perspective because it hints at the CMB's last scattering surface being the ``inverse'' of the sun's own last scattering surface; and the edge of the observable Universe as an event horizon, similar to black hole's. \textbf{Credit:} Pablo Carlos Budassi. \\

\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:structure}} on page~\pageref{chap:structure}:  \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Map of the distribution of galaxies centered on the Milky Way. \textbf{Credit:} 2dF GRS. \\

\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:LyaForest}} on page~\pageref{chap:LyaForest}:  \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Intergalactic neutral Hydrogen gas distribution inferred from the Ly-$\alpha$ forest measured in quasars with the eBOSS spectrograph. Color encodes gas density. \textbf{Credit:} An\u{z}e Slosar and Andreu Font Ribera. \\

\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:Simulations}} on page~\pageref{chap:Simulations}:  \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Intergalactic gas distribution simulated by our hydrodynamics simulations. The simulation box is a comoving cube of $100~\mathrm{Mpc}$ in length with periodic border conditions, containing $768^3$ dark matter, and $768^3$ gas particles. \textbf{Credit:} Julien Baur. \\

\flushleft{
\textbf{Background Figure of Chapter~\ref{chap:results}} on page~\pageref{chap:results}:  \\
}
\vspace{0.2cm}
\hspace{0.6cm}
Baryon gas distribution in dark matter halos, in a pure cold dark matter cosmology (top) and a pure warm dark matter cosmology (bottom). Produced by the \textsf{Aquarius} project using the \textsf{Millenium} simulations, part of the Virgo Consortium: \url{http://www.virgo.dur.ac.uk/}. \textbf{Credit:} \cite{Lovell_wdm_halo}.
